\chapter*{Acknowledgements}
I would like to express my gratitude to the following people and organisations: \newline \\
The National Research Foundation (NRF) for funding the bulk of my M.Sc. degree. \newline 
Rhodes University and the Levenstein family for the provision of bursaries. \newline 
A special note of thanks to Mr. John Gillam at the Rhodes University Postgraduate funding office for all his help with organising funding. \newline 
My supervisor, Dr. Iain Paterson, for his valuable feedback and encouragement. Iain's enthusiasm is contagious! \newline
My co-supervisor, Dr. Shelley Edwards, for her valuable advice, and assistance in the Zoology and Entomology Molecular Lab (ZEML) at Rhodes University. \newline 
Prof. Martin Hill for all his support, positivity, and encouragement. The Entomology Department at Rhodes University is incredibly lucky to have someone as resourceful and passionate as he is. \newline 
The students and staff at the Centre for Biological Control (CBC) and the Department of Zoology and Entomology at Rhodes, with a special thanks to Mrs. Jeanne van der Merwe for her assistance in organising payments and other administrative work. \newline 
The Central Analytical Facilities (CAF) at Stellenbosch University for the fragment analysis of ISSR samples, with a special thanks to Mrs. Ren\'e Veikondis. \newline 
My office mates: Ant, Evans, and Megan, for all the laughs and fun we have had. \\
My flat mates: Elisa, Glyn, and Olivier, for their friendship. \\
Lastly, my mother, and the family and friends who have shown their love and support. 